---
title: "Mini-Project 3"
author: "Yifan Ma & Meghan Suslovic"
date: "April 9, 2018"
output: 
  html_document:
    code_folding: hide
    df_print: paged 

---

MacLeish currently has two campsites - one large group site closer to the building and one remote campsite with two tent platforms about one mile from the parking area. We would like to develop one additional campsite that is approximately half a mile walk from the parking area, within 200’ of a stream or other source of water, in forest that is unlike the forest in the two other campsites, relatively flat, and at least 500’ from any research area or any element of the Challenge Course. Propose two new campsite locations for our consideration.
Supporting data includes:
-Existing trails shapefile
-10’ contour elevation data
-vegetation type shapefile
-hydrology (streams, wetlands, etc.) shapefile
-Research locations shapefile
-Challenge course element locations shapefile
-Property Boundary shapefile

Old field forest== multiflora rose or bittersweet very hard to clear
lean to=$3,000, hard to deliver supplies for construction
more like two tent platforms and picnic table

**Title:**
In tents Camping at MacLeish! 
Where to construct a third campsite at MacLeish Field Station in Whately, MA

Smith College's MacLeish Field Station is looking to create a third campsite for students and visitors to utilize. The client, Field Station Manager Reid Bertone-Johnson, stipulated a number of specific requirements  for the new campsite which include:
-within 1/2 mile from the parking lot
-no further than 200 ft from a water source
-at least 500 ft from any research area or Challenge Course element
-not in the same type of forest as the other two campsites (i.e. not______)
-relatively flat
Our task was to analyze spatial data and factor in the client's above criteria in order to come up with two recommendations for a third campsite location. All of the data we used comes from the MacLeish package and specifically the macleish_layers data object. By constructing buffers around the parking lot, streams, research areas, and challenge course elements, we determined that the new campsite would have to be in the southern half of the Field Station. 
  



```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo=TRUE)
```

```{r}
library(tidyverse)
library(leaflet)
library(dplyr)
library(etl)
library(macleish)
library(sf)
```

```{r}
buildings_4326 <- macleish_layers[["buildings"]] %>%
  st_as_sf() %>%
  st_transform(4326)

trails_4326 <- macleish_layers[["trails"]] %>%
  st_as_sf() %>%
  st_transform(4326)

streams_4326 <- macleish_layers[["streams"]] %>%
  st_as_sf() %>%
  st_transform(4326)

wetlands_4326 <- macleish_layers[["wetlands"]] %>%
  st_as_sf() %>%
  st_transform(4326)

research_4326 <- macleish_layers[["research"]] %>%
  st_as_sf() %>%
  st_transform(4326)

boundary_4326 <- macleish_layers[["boundary"]] %>%
  st_as_sf() %>%
  st_transform(4326)

cc_4326 <- macleish_layers[["challenge_courses"]] %>%
  st_as_sf() %>%
  st_transform(4326)

forests_4326 <- macleish_layers[["forests"]] %>%
  st_as_sf() %>%
  st_transform(4326)

boundary_4326 <- macleish_layers[["boundary"]] %>%
  st_as_sf() %>%
  st_transform(4326)

contour_4326 <- macleish_layers[["contours_3m"]] %>%
  st_as_sf() %>%
  st_transform(4326)


```



```{r, echo = FALSE, eval = FALSE}
macleish_map <- leaflet() %>%
  addTiles() %>%
  addPolygons(data = buildings_4326, weight = 1) %>%
  addPolylines(data = trails_4326, weight = 1, color = "brown") %>%
  addPolylines(data = streams_4326, weight = 2, color = "blue") %>%
  addPolygons(data = wetlands_4326, weight = 1, color = "darkgreen") %>%
  addPolygons(data = research_4326, weight = 1, color = "black") %>%
  addPolygons(data = forests_4326, weight = 1, color = "lightgreen")%>%
  addPolygons(data = macleish_layers[["contours_3m"]], color = "red") 


macleish_map  

```

```{r}
proj4_aea <- "+proj=aea +lat_1=29.5 +lat_2=42.5 +lat_0=37.5 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"

b_streams <- streams_4326 %>%
  st_transform(proj4_aea) %>%
  st_buffer(dist = 60.96) %>%
  st_transform(4326) 
```

```{r}
b_research <- research_4326 %>%
  st_transform(proj4_aea) %>%
  st_buffer(dist = 152.4) %>%
  st_transform(4326)

b_research_union <- st_union(b_research)
```

```{r}
b_challenge <- cc_4326 %>%
  st_transform(proj4_aea) %>%
  st_buffer(dist = 152.4) %>%
  st_transform(4326)

b_challenge_union <- st_union(b_challenge)
```

```{r}
parking_lot <- data.frame(lon = -72.680663, lat = 42.448013) 
  
parking_lot_sf <- st_as_sf(parking_lot, coords = c("lon", "lat"), crs = 4326) %>%
  st_transform(proj4_aea) %>%
  st_buffer(dist = 840.672) %>%
  st_transform(4326)

campsite <-  data.frame(lon = -72.678154, lat = 42.450976)
r_campsite <- data.frame(lon = -72.679581, lat = 42.458549)

campsite_sf <- st_as_sf(campsite, coords = c("lon", "lat"), crs = 4326)
r_campsite_sf <- st_as_sf(r_campsite, coords = c("lon", "lat"), crs = 4326)

n_campsite <- data.frame(lon = -72.673847, lat = 42.449276)
#n_campsite2 <- data.frame(lon = -72.678154, lat = 42.450976)

n_campsite_sf <- st_as_sf(n_campsite, coords = c("lon", "lat"), crs = 4326)
#n_campsite2_sf <- st_as_sf(n_campsite2, coords = c("lon", "lat"), crs = 4326)

```

```{r}
forests_pal <- colorFactor(palette = "Greens",
  domain = forests_4326$Sheet1__Na)
```

### Color Coded Macleish Base Map
```{r}
macleish_map <- leaflet() %>%
  addProviderTiles(providers$CartoDB.Positron)%>%
  addPolygons(data = b_streams, weight = 1) %>%
  addPolygons(data = b_research_union, color = "red", weight = 1) %>%
  addPolygons(data = b_challenge_union, color = "yellow", weight = 1) %>%
  addPolygons(data =parking_lot_sf, color = "grey", weight = 1) %>%
  addPolygons(data = forests_4326, weight = 1, color = "darkgreen") %>%
  addMarkers(data = campsite_sf, popup = "Group Campsite") %>%
  addMarkers(data = r_campsite_sf, popup = "Remote Campsite")

macleish_map
```

######Red: 500 feet from any research area
######Yellow: 500 feet from any element of challenge course 
######Blue: 200 feet from streams 
######Green: land covered with various types of forests.
######Grey: Half a mile from parking lot




### Possible Candidate Area
```{r}
macleish_map_2 <- leaflet() %>%
  addProviderTiles(providers$CartoDB.Positron)%>%
  addPolygons(data = b_streams, weight = 1, color = "blue") %>%
  addPolygons(data = forests_4326, weight = 1, color = "blue") %>%
  addPolylines(data = macleish_layers[["contours_3m"]], color = "blue", weight = 0.5) %>%
  addMarkers(data = campsite_sf, popup = "Group Campsite") %>%
  addMarkers(data = r_campsite_sf, popup = "Remote Campsite") %>%
  addMarkers(data = n_campsite_sf, popup = "New Campsite 1" ) %>%
  addPolygons(data = b_research_union, color = "red", weight = 1) %>%
  addPolygons(data = b_challenge_union, color = "red", weight = 1) 

macleish_map_2
```

######Red: Areas to avoid
######Blue: Areas open to consideration ( The darker shade of blue, the more likely the requirements for the new campsites are met)




### Forest Type and Candidate Area
```{r}
macleish_map_f <- leaflet(data = forests_4326) %>%
  addProviderTiles(providers$OpenTopoMap)%>%
  addPolygons(weight = 1, fillOpacity = 1, color = ~forests_pal(Sheet1__Na)) %>%
  addMarkers(data = campsite_sf, popup = "Group Campsite") %>%
  addMarkers(data = r_campsite_sf, popup = "Remote Campsite" ) %>%
  addMarkers(data = n_campsite_sf, popup = "New Campsite 1" ) %>%
  addLegend("bottomright",pal = forests_pal, values = ~Sheet1__Na, title = "Forest Type", opacity = 1  )

macleish_map_f
```

